|

### 2024-10-26 docs/paper.qmd
presentation changes for brown bag
Pre SSRN

---
title: |
  | Accountants' Attitudes Towards Open Science^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management. We thank Kris Hardies as well as audiences at University of Antwerp, Humboldt University Berlin, and WHU for providing helpful feedback. Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged. This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: 
  - name: Joachim Gassen
    email: gassen@wiwi.hu-berlin.de
    affiliation: Humboldt-Universität zu Berlin
  - name: Jacqueline Klug
    email: Jacqueline.Klug@whu.edu
    affiliation: WHU Otto Beisheim School of Management
  - name: Victor van Pelt
    email: Victor.vanPelt@whu.edu 
    affiliation: WHU Otto Beisheim School of Management
date: last-modified
date-format: long
execute:
  echo: false
  message: false
  warning: false
format:
  pdf:
    documentclass: article
    number-sections: true
    colorlinks: true
    papersize: letter
    fig-pos: H
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes

@@

header-includes:
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \setlength{\skip\footins}{2em}
  - \usepackage[hang]{footmisc}
  - \setlength{\footnotemargin}{1em}
  - \usepackage{pdfpages}
  - \usepackage{pdflscape}
  - \usepackage{csquotes}
  - \renewcommand{\mkbegdispquote}[2]{\itshape}
---

@@

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv("../data/external/invited_authors_anon.csv", show_col_types = FALSE)

@@

source("../code/obs_data_analyses.R")
```

```{=tex}
\thispagestyle{empty}
\begin{abstract}
\singlespace
Surveying a sample of scholars who have published in leading accounting journals, we document that we accounting researchers are more skeptical about the reproducibility of our influential findings than researchers from other social science areas are about theirs. Also, we are less familiar with the public sharing of research materials (data, code, and research procedures) and have less experience with pre-registrating our study designs, two prominent open science measures to increase the reproducibility of research. Our respondents state that they are open to sharing and would likely share research materials under a hypothetical scenario, regardless of provided rationale and scope. They also believe that other accounting researchers, as well as editors, are in favor of research material sharing. However, they are skeptical about the actual prevalence of research material sharing in the accounting research community. In addition, they are more reluctant than researchers from neighboring fields to pre-register their study plans. We interpret this descriptive evidence as indicating an "accounting open science dilemma" and suggest strategies for addressing it.
\end{abstract}
```

```{=tex}
\vspace{0.5cm}
\begin{center}
\textbf{Preliminary and Incomplete}
\end{center}
\vspace{0.75cm}
\begin{flushleft}
\textbf{Keywords}: Accounting Research, Open Science, Reproducibility, Pre-Registration, Survey \newline
\textbf{Data Availability}: Data available in code repository \newline
\textbf{Code Repository}: \href{https://github.com/joachim-gassen/osacc}{https://github.com/joachim-gassen/osacc}  \newline
\textbf{Survey Dashboard}: \href{https://jgassen.shinyapps.io/osacc/}{https://jgassen.shinyapps.io/osacc} \newline
\textbf{Declaration of Interest}: The author(s) declare(s) that they have no conflict of interest \newline
\end{flushleft}
```
\pagebreak

@@

Cumulative science builds on reproducible research.[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2000; @G_2023; @S_2023; @CGL_2023], scholars have diagnosed shortcomings in reproducibility and advocated open science methods like public sharing of research materials and the pre-registration of study plans as potential strategies to improve the reproducibility of our work. Prior work across the social sciences has documented an overall uptake of open sciences approaches across several disciplines [@FLCPSWMBP_2023]. We contrast these findings with a survey that we conducted among accounting researchers to explore the perceptions and attitudes toward open science in our field.

[^1]: While in the survey itself, we use the term reproducibility without an exact definition, throughout this article, we follow the notion of @NSF_2015 to define reproducibility as the "ability of a researcher to duplicate the results of a prior study using the same materials and procedures as were used by the original investigator" while replicability "refers to the ability of a researcher to duplicate the results of a prior study if the same procedures are followed but new data are collected". For a more in-depth discussion of the related terminological debate, see @GFI_2016. The key reason why we do not provide an exact definition in the survey is that the differences between reproducibility and replicability are subtle and vary across accounting subfields. For archival studies, reproducibility and replicability should be essentially the same, while for experimental studies they clearly differ.

Based on the responses of `r nrow(sd)` published accounting researchers, we find that our attitudes towards open science clearly differ from those of other researchers in the social sciences. Most prominently, we tend to hold a generally more critical view of the reproducibility of our influential work. Compared to the fields of economics and sociology, for example, we are about half a point more skeptical about the reproducibility of the influential work in our field on a 5-point Likert scale. Exploring this assessment across our respondents' demographics, we find this skepticism to be relatively stable. Analytical and qualitative researchers are somewhat more pessimistic than the other methodologies. Analytical researchers tend to be particularly more critical of research that uses non-analytical methods.

Given this finding, one would expect accounting researchers to take a more proactive stance and embrace two prominent open science approaches that methodological work has identified to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans. Turning first to the public sharing of research materials, we document that, again, compared to researchers from other social science areas, we accounting researchers are somewhat less familiar with this activity. Also, we find it somewhat less important. Familiarity is generally largest for respondents using archival, field, and experimental methods and smallest for respondents using qualitative methods, which also perceive sharing as less important.

Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in our perceived (prescriptive) importance of research material sharing, our stated willingness to share research materials, and our (descriptive) perception about actual sharing behavior. In a hypothetical scenario, the average stated likelihood for sharing research materials by our respondents is relatively high (i.e., 72%), and this likelihood is more or less unaffected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope (public versus private sharing).[^2] Also, 50% of our respondents state that they, at least sometimes, publicly share their research materials. In addition, our respondents believe that about 44% of us favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials.

All this sounds comforting and consistent with a general supportive stand of the accounting community towards public research material sharing. However, when asked about respondents' perceptions about actual sharing behavior, the percentage comes down to a much more sobering 28%. This sober number and the gap it reveals differ significantly across the different accounting methodological areas. Analytical researchers have the narrowest gap (they expect 43% of accounting researchers to be in favor and 38% to actually share research materials). Archival researchers, in turn, have the widest gap (45% expected to be in favor versus 24% expected to actually share). The overall lowest numbers are again reported by qualitative researchers (36% versus 18%).

Using observational data from a country-stratified random sample of `r nrow(authors)` authors from our target population to contrast these perceptions with actual behavior, we find at least some evidence for research material sharing for 39 % of this random sample. This number is largely in line with the self-reported figures but masks that research material sharing in accounting seems to be largely an occasional compliance activity: Only for 7.5 % of the papers that we analyze we find evidence for research material sharing and when we exclude Journal of Accounting Research and Management Science, two journals with data and code policies in place, the share of authors for which we document research material sharing evidence drops from 39 to 23 %.

In light of these numbers, it is a logical next step to explore the main reasons against sharing research materials. Overall, the most commonly stated reasons for not sharing research materials are the proprietary nature of the used data (56% of respondents give this reason), the time it takes to make materials available (30%), and the fear of being scooped when materials become publicly available (23%). Additionally, 34% of respondents state that there is no need for sharing as their data is already publicly available. Unsurprisingly, the reasons clearly differ across methods. For qualitative researchers, deidentification problems are very prominent (46%), and analytical researchers consider the time it takes to make materials available far less of a reason than researchers using other methods (i.e., 9.5% versus 30% overall).

Regarding pre-registration, it seems that we accounting researchers are at least as familiar with the concept as other social science researchers. However, our respondents report that they started using it later than other social science researchers (roughly two years) and that they use it less frequently (17% versus 27%). Our trust in pre-registered work is generally comparable with other social scientists but significantly lower than the trust levels of researchers in Psychology (the field that reports the highest usage rates of pre-registration). A detailed look into differences among the different methodological fields within accounting also reflects this, as we find that experimental researchers use pre-registration the most (28%) and express the strongest belief that the practice increases the trustworthiness of research.

Taken together, our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work, and the ability of research material sharing and pre-registration to improve it. This results in these tools currently being less established in the accounting domain than in other fields. In addition, the challenges that hinder reproducibility and the potential effectiveness of open science tools vary across methodological paradigms. Qualitative research faces different challenges than archival quantitative work, and they both differ again from experimental studies. We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.

## Survey Methodology and Variable Measurement

### Survey Design and Administration

To collect the attitudes of accounting researchers towards open science, we conducted a survey among members of the academic accounting community. The survey has been designed using oTree [@CSW_2016]. To recruit respondents for our survey, we identified authors who published in the "Top 6" accounting journals, i.e., Accounting, Organizations and Society, Contemporary Accounting Research, Journal of Accounting and Economics, Journal of Accounting Research, Review of Accounting Studies, The Accounting Review, over the period 2016 to 2021. We chose these six accounting journals because they are commonly known to be top accounting journals within the academic accounting community. We realize that this is not an exhaustive list and that there are divergent views about journals within the accounting community. Yet, we believe that, taken together, these journals provide us with a representative list of publishing accounting academics. We started compiling the list of authors from 2016 because this is the year that Open Science and, more specifically, the reproducibility of research became a more widespread topic of debate among academics within the social sciences and, presumably, accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017]. After receiving approval from an ethical review board, also guaranteeing the anonymity of the participating respondents, we sent out initial invitations and a total of three reminders. We allowed potential respondents to opt out of future emails every time we reached out to them. Please see Appendix A for the invitation emails.

@@

Table 1 displays our sample selection procedures. Of the 2,660 potential respondents we identified, we excluded 118 for various reasons.[^3] Furthermore, for 206 emails bounced, we received a notification that the email address was unreachable. Of the remaining 2,336 successfully reached accounting researchers, 391 started the study (15,4% of the total emails sent), 254 partially completed the study (10,9% of the total emails sent), and 222 fully completed the study (8,7% of the total emails sent).[^4] Table 2 displays our final sample's demographics and characteristics. Panel A reveals that the majority of the respondents are male, 35 years or older (87.8%), specialize in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).

[^4]: As the dependent variable of our hypothetical scenario analysis outlined below is the first data we collect, 254 is the sample size for this analysis. For the descriptive analyses, we settle for the number of participants that answered the respective question and, if applicable, also provided the necessary demographics for cross-sectional splits. Depending on this, the sample sizes for the descriptive analyses vary from 222 to 229 responses.

@@

Panel B of Table 2 contrasts our respondent sample with our sampling population. Given the anonymity of our response and the data that we can collect about our population, we can only compare the geographic dispersion of our sample. Panel B reveals that, in particular, researchers from North America and Europe are over-represented, and researchers from Asia are under-represented in the sample. Given that response rate assessment is inherently challenging, we generally avoid speculating about potential reasons for this sampling imbalance. However, it seems likely that the study's all-European author team might have positively influenced the European response. While we control for geographical effects in our response (not-tabulated but available using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.

### Variable Measurement

>>>>

---
title: |
  | How does the Accounting Research Community
  | Think About Open Science?^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management. We thank Kris Hardies as well as audiences at University of Antwerp, BI Norwegian Business School, Humboldt University Berlin, Stanford University, and WHU for providing helpful feedback. Scott Summers and David Wood thankfully provided data from the BYU Accounting Research Rankings. Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged. This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: 
  - name: Joachim Gassen
    email: gassen@wiwi.hu-berlin.de
    affiliation: Humboldt-Universität zu Berlin
  - name: Jacqueline Klug
    email: Jacqueline.Klug@whu.edu
    affiliation: WHU Otto Beisheim School of Management
  - name: Victor van Pelt
    email: Victor.vanPelt@whu.edu 
    affiliation: WHU Otto Beisheim School of Management
date: last-modified
date-format: long
execute:
  echo: false
  message: false
  warning: false
format:
  pdf:
    documentclass: article
    number-sections: true
    colorlinks: true
    papersize: letter
    fig-pos: H
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes

@@

header-includes:
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \setlength{\skip\footins}{2em}
  - \usepackage[hang]{footmisc}
  - \setlength{\footnotemargin}{1em}
  - \usepackage{pdfpages}
  - \usepackage{pdflscape}
  - \usepackage{csquotes}
  - \usepackage{lscape}
  - \usepackage{graphicx}
  - \usepackage{pdflscape}
  - \renewcommand{\mkbegdispquote}[2]{\itshape}
  - \usepackage{longtable}
  - \usepackage{geometry}
  - \geometry{a4paper, margin=1in}
  - \usepackage{setspace}
---

@@

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv("../data/external/invited_authors_anon.csv", show_col_types = FALSE)
byu <- read_csv("../data/external/byu_author_data_anon.csv", show_col_types = FALSE)

@@

source("../code/obs_data_analyses.R")

gt_add_header_mpage_table <- function(x) {
  x <- sub("\\\\midrule", "\\\\midrule \\\\endhead", x)
  x
}

```{=tex}
\thispagestyle{empty}
\begin{abstract}
\singlespace
To understand how the accounting research community thinks about open science, we survey a sample of scholars who have published in leading accounting journals. Building on a voluntary disclosure-themed discussion of the costs and benefits of open accounting research, we document that accounting researchers tend to be more skeptical about the reproducibility of their influential findings than researchers from other social science areas are about theirs. Also, they are less familiar with the public sharing of research materials and pre-register their study designs less often. While they believe that accounting researchers in general and editors in particular favor research material sharing, they are skeptical about its actual prevalence in the accounting research community. We contrast these survey results with observational data, documenting that research material sharing is indeed relatively rare and often linked to journals with data and code sharing policies. We interpret this descriptive evidence as indicating an "accounting open science dilemma" and suggest strategies for addressing it.
\end{abstract}
```
```{=tex}
\vspace{0.5cm}
\begin{flushleft}
\textbf{Keywords}: Accounting Research, Open Science, Reproducibility, Research Material Sharing, Pre-Registration, Survey \newline
\textbf{Data Availability}: Data available in code repository \newline
\textbf{Code Repository}: \href{https://github.com/joachim-gassen/osacc}{https://github.com/joachim-gassen/osacc}  \newline
\textbf{Survey Dashboard}: \href{https://jgassen.shinyapps.io/osacc/}{https://jgassen.shinyapps.io/osacc} \newline
\textbf{Declaration of Interest}: The author(s) declare(s) that they have no conflict of interest \newline
\end{flushleft}
```
\pagebreak

@@

Cumulative science builds on the reproducibility of research, which is the ability to recreate the results of prior studies using the same materials as were used by the original researchers [@NSF_2015].[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2000; @G_2023; @S_2023; @CGL_2023], scholars have diagnosed shortcomings in reproducibility and advocated the use of various open science methods. Open science implies conducting research in ways that allow others to collaborate and contribute. Two central open science methods that have been put forward as strategies to improve the reproducibility of our work are the public sharing of research materials and the pre-registration of study plans. Over the last years, there has been a significant uptake of these open sciences methods in social science areas outside of accounting [@FLCPSWMBP_2023].

Research material sharing and pre-registrations can be understood as disclosure mechanisms that allow researchers to contribute public goods to the research community while also signaling the quality of their work. However, limited individual benefits and significant direct as well as indirect costs make it likely that researchers, on average, will rationally under-engage in these activities, potentially resulting in a socially sub-optimal under-provision of public research materials and on overall lacking research transparency. Following these thoughts and building on prior literature in neighboring fields, we conduct a survey among accounting researchers to explore the perceptions and attitudes towards open science in our field.

Based on the responses of `r nrow(sd)` published accounting researchers, we find that attitudes towards open science clearly differ from those of other social science researchers. Most prominently, accounting researchers tend to hold a generally more pessimistic view of the reproducibility of influential work within their field. Compared to economists and sociologists, for example, accounting researchers are about half a point more skeptical on a 5-point Likert scale. Exploring this assessment across the respondents' demographics, we find this skepticism to be relatively stable. Analytical and qualitative researchers are somewhat more pessimistic. Analytical researchers tend to be particularly more critical of research that uses non-analytical methods.

Given this finding, one would expect accounting researchers to take a proactive stance and embrace two prominent open science methods that are expected to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans. Turning first to the public sharing of research materials, we document that, again compared to researchers from other social science areas, accounting researchers are somewhat less familiar with this activity and assess it to be somewhat less important. Familiarity is largest for respondents using archival, field, and experimental methods and lowest for respondents using qualitative methods, who also perceive the sharing of research materials as less important.

Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in accounting researchers' perceived (prescriptive) importance of research material sharing, their stated willingness to share research materials, and their (descriptive) perception about actual sharing behavior in the accounting research community. 57% of our respondents state that they, at least sometimes, publicly share their research materials. In addition, our respondents believe that about 44% of them favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials. Although this sounds comforting and consistent with a general supportive stance of the accounting community toward research material sharing, the percentage comes down to a much more sobering 28% when respondents are asked about actual sharing behavior in the accounting research community. This assessment and the gap it reveals differ significantly across methodological areas. Analytical researchers have the most narrow gap (they expect 43% of accounting researchers to be in favor and 38% to actually share research materials). Archival researchers, in turn, have the widest gap (45% expected to be in favor versus 24% expected to actually share). The overall lowest numbers are again reported by qualitative researchers (36% versus 18%).

Regarding pre-registration, accounting researchers seem as familiar with the concept as other social science researchers. However, our respondents report that they started using it later than other social science researchers (roughly two years) and that they use it less frequently (17% versus 27%). Their trust in pre-registered work is generally comparable with other social science researchers but significantly lower than the trust levels of researchers in Psychology (the field that reports the highest usage rate of pre-registration). A detailed look into differences across methodological fields also reflects this, as we find that experimental researchers use pre-registration most (28%) and express the strongest belief that it increases the trustworthiness of research.

To contrast these perceptions from our survey with actual behavior, we gather additional observational data from a country-stratified random sample of `r nrow(authors)` authors of our target population. We find evidence for at least some form of research material sharing for 39% of the authors in this sample. This number is similar to the self-reported perception of actual research material sharing in our survey (i.e., 38%). However, when we inspect the observational data further, we find that research material sharing in accounting is largely an occasional compliance activity. For instance for 7.5% of the papers written by the authors in the observational data show evidence for research material sharing. Also, when we exclude Journal of Accounting Research and Management Science, two journals with data and code sharing policies, the share of authors for which we document at least some form of research material sharing drops from 39% to 23%. Furthermore, we document very few pre-registrations in our observational data, and all are linked to the Registered Report Initiative of the Journal of Accounting Research.

In light of these numbers, a logical next step is to explore the main rationales for and against sharing research materials. We do so based on a short experimental design using a hypothetical scenario and by using our survey data.[^2] In our hypothetical scenario involving a fellow researcher requesting access to participants' research materials, our participants state that they would be very likely to share on average (mean probability is 72%). We find no evidence that this probability is affected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope of the sharing decision (public versus private sharing). Based on the verbal response of our participants, researchers tend to share their materials as they believe that this improves the quality of their research and of research in general. Also, they share because they want to support their fellow researchers. The most commonly stated reasons for not sharing research materials are the proprietary nature of the data used (56% of respondents give this reason), the time it takes to make materials available (30%), and the fear of being scooped when materials become publicly available (23%). The reasons differ across methods. For qualitative researchers, deidentification problems are very prominent (46%), and analytical researchers consider the time it takes to make materials available far less of a reason than researchers using other methods (i.e., 9.5% versus 30% overall).

Taken together, our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work, and the ability of research material sharing and pre-registration to improve it. This is consistent with these tools currently being less established in the accounting domain than in other fields. The challenges that hinder reproducibility and the potential effectiveness of open science methods vary across methodological paradigms. Qualitative research faces different challenges than archival quantitative work, and they both differ again from experimental studies. We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.

## Expectations and Study Design

### Costs and Benefits of Open Accounting Research

Accounting is a field within the social sciences. As such, many of the arguments that have been developed with regard to the costs and benefits of open science in general [@AM_2019; @ABC_2021; @G_2022; @FLCPSWMBP_2023] also apply to the field of accounting. In the following, we present and extend some of these thoughts in a voluntary disclosure framework [@BCLW_2010]. For this purpose, our discussion will be primarily anchored on research material sharing (the main focus of our study) but should largely extend to pre-registration. Understood as a disclosure activity related to underlying research, publicly available research materials constitute a public good. To the extent that they are reusable, they accelerate scientific discoveries, improving the quantity and very likely also the quality of research. Even if they are not really reusable or reusing them would be prohibitively costly, they still reduce the costs of reproducing the original work, thereby reducing assurance costs. As the work in auditing [e.g., @S_1980] posits, reduced auditing costs (easier reproduction) should lead to an overall increase in audit quality (more and better reproductions) resulting in better financial reporting quality (better research).

This means that similar to other disclosure activities, sharing research materials does not necessarily benefit the producer but the research community at large. While intrinsic motivation for good research can be expected to be a strong determinant for individuals self-selecting into the academic accounting profession, one can still expect accounting researchers to under-engage in research material sharing because the production costs are mostly private while the benefits are mostly public. So, are there any private benefits of research material sharing? Besides the warm glow of helping others, research material sharing likely improves the quality of the sharing individual's research output. First, it increases the likelihood that mistakes, conditionally on being present, are being detected. As it seems safe to assume that such incidents impose a cost on sharing researchers, this should increase their incentives to increase research quality prior to sharing. Second, if research materials are shared relatively early, the sharing researcher can directly benefit from community feedback prior to the ultimate publication of the study. Finally, uncovered mistakes are an important learning opportunity, likely improving research quality in the long run.

Based on these arguments, there are reasons to believe that voluntary research material sharing can act as a signal for research quality, creating an incentive for researchers to use it to signal the quality of their work in the publishing and career process. In ideal circumstances, we should obtain the well-known unraveling result where researchers even share and improve low-quality research because the research community would otherwise assume the worst [@M_1981]. One critical obstacle to the unraveling result are disclosure costs [@V_1983], also known as proprietary costs in the contemporary disclosure literature. Thus, for research materials sharing to be viable it is important that the costs of sharing are sufficiently low, especially for researchers that produce high quality work. Thus, it critically hinges on the above quality assurance process. Also, it depends on the direct and indirect costs of research material sharing to be bearable and to be at least comparable for high and low quality researchers.

The direct costs of research material sharing can be sizable. Preparing data, code and research procedures for dissemination requires time. While this time can be expected to also have a quality improvement effect (see above), at least some of the documentation work and code refactoring to increase accessibility and reusability creates costs that will not directly pay off on the quality of the underlying work. Another important factor to consider is the cost of maintaining publicly available materials. While some replication packages or similar materials are static in nature and require only limited maintenance, data and code packages can require ongoing updating and support activities. One important aspect of maintenance costs is that they increase significantly with public demand. As demand is directly linked to the scientific impact of the underlying work it can be argued that high maintenance cost sharing activities are likely to also be high benefit activities.

The indirect costs of research material sharing are first and foremost linked to the quality assurance process outlined above. Flaws in publicly shared research materials can trigger more behavioral effects (shame, regret) but also reputation costs. Another important aspect are proprietary costs from scientific competition. While likely to be positive from the societal perspective, the indirect individual costs of being "scooped" for an interesting follow-up project can be sizable. Finally, there is also the possibility of unethical misuse of shared research materials. Malevolent researchers might use shared materials without proper attribution or use it with a strategy of "reverse p-hacking", meaning creating reproductions or replications that communicate a biased picture of the overall evidence to increase their chances for publication.

Rational researchers can be expected to voluntarily share research materials when their private benefits outweigh their private costs. Whether this happens will critically depend on whether the signaling mechanism outlined above unfolds. In a credence good market like research, signaling is a key mechanism to avoid market failure. Based on the discussion above, a critical aspect could be the proprietary cost of competition as one could argue that this cost is higher for high quality researchers with innovative ideas than for low quality researchers that will likely face limited demand for their materials. Also the risks of reputation costs or misuse of materials could be higher for high quality researchers. On the other hand, it can be argued that direct costs should be lower for high quality researchers because of superior skills. Finally, outside options should be generally higher for high quality researchers meaning that they face higher opportunity costs of their time but also less competitive pressure to keep their materials private.

The discussion should sound somewhat familiar to those that study voluntary disclosures by firms. What is different from our traditional firm-setting is that most researchers are not acting as entrepreneurs. Instead, they are employed by academic institutions or act as civil servants. This can to some extend mute the relevance of the benefits and the costs outlined above, at least for those researchers that hold tenured positions. In addition, the employing institutions might also interact with the decision whether or not to make research materials available. They are designing performance and tenure evaluation criteria that incentivize researchers. Also, they compensate researchers for their time and they provide them with infrastructure that influences and at times drastically reduces the direct costs of research material sharing. They might even hold property rights on the intellectual capital that their employees generate. Based on the public announcements of many leading academic institutions, it seems as if these are generally advocating the positive externalities of research material sharing. However, the incentive systems designed by these institutions appear at least in parts inconsistent with these announcements, as they are valuing individual research achievements in form of publications and only rarely publicly available research materials.

Finally, publishers and journals are influential for research material sharing decisions as well. Leading journals have established demanding data and code sharing guidelines, essentially transforming the voluntary disclosure decision to a mandatory disclosure requirement. While journals also compete for the best papers and it is an interesting question how this competition affects the dissemination of data and code sharing guidelines, it seems as if imposing mandatory disclosure rules is a classic response to overcome the diagnosed public good problem.

### Research Questions and Survey Design

Following the discussion above, we designed our survey to address three overlapping research questions.

1.  How does the accounting research community assess the reproducibility of their influential work?

2.  What are the views of the accounting research community about research material sharing and pre-registration, two prominent open science methods to increase the reproducibility of research?

3.  What are the (perceived) costs and benefits of research material sharing?

The first two questions are descriptive in nature. Assuming that the signaling mechanism above or other incentives have not succeeded in removing all insecurity about the reproducibility of influential accounting work, we expect to find some variation in our response with regard to research question one. More importantly, we want to compare the response of our sample with responses by researchers from other social science fields. The second question explores whether accounting researchers believe that research material sharing and pre-registration are viable strategies to increase the reproducibility of research. Again, comparing the views of accounting academics with the views of neighboring fields will be instrumental here.

The third question strives to understand the potential causes behind these assessments. Using a small experimental component, our survey tests whether two aspects of a hypothetical sharing request, its rationale (collaboration or control) and its scope (public versus private), affect the stated hypothetical likelihood of sharing. Our motivation for the treatments is that the rationale should shift the focus from benefits (collaboration) to costs (control) while the scope treatment should manipulate the salience of indirect costs. Besides studying the effect of these two experimental treatments, we also use verbal and structured survey response data to uncover perceived benefits and costs from research material sharing.

To verify whether the assessments provided by our survey participants are consistent with their behavior in the field, we also conduct an observational study that uses data from 100 authors of our target population to contrast the survey response with the actual research material sharing and pre-registration behavior in the field.

To ensure that our findings with respect to research questions one and two are comparable with related prior work, we adapted key questions from the Survey of Open Science Practices and Attitudes in the Social Sciences [@FLCPSWMBP_2023], published in Nature Communications. Similar to our survey, this study solicits the views of published researchers and PhD students on reproducibility, research material sharing, and pre-registration. However, there are key differences between the depth and target audience of our study and the study of @FLCPSWMBP_2023, warranting some adjustments. The latter lasted approximately 45 minutes and had a compensation element rewarding respondents for their participation. Our study, in contrast, is anonymous and has been designed to be completed in less than 10 minutes. It includes only mild incentivization in the form of a donation to UNICEF. Regardless of our adaptions, the ordering, phrasing, and answering scales of questions in our survey are similar. The adaptions enable us to considerably shorten the survey and to ensure that accounting researchers can relate the questions to their commonly accepted research practices. We pre-tested our adapted questions among a group of doctoral students specializing in accounting, which indicated no issues with the adapted questions. Appendix C includes a matching table providing an overview of every question and answer scale that we adapted from @FLCPSWMBP_2023.

Our survey has been designed using oTree [@CSW_2016]. The first stage of the survey includes questions about respondents' views on publicly sharing research materials, which we describe as comprising data, code, and research procedures. Specifically, we ask respondents about their familiarity with the public sharing of research materials and their views of its importance. We also ask them about their perceptions of the prevalence of sharing in the accounting research community, how often they tend to share, and whether they plan to share in the future. Conditional on whether respondents indicate that they do not always share, we also ask them for the reasons behind not sharing. Lastly, we ask respondents to estimate what percentage of accounting researchers favor sharing and their approximation of the percentage of editors of the top six accounting journals that believe sharing increases the value of a manuscript.

The second stage of the survey features a selection of questions about respondents' views on reproducibility and pre-registration, which we also borrowed and adapted from @FLCPSWMBP_2023. First, we ask respondents about their confidence in the reproducibility of accounting research. We also asked them about their subfield within the domain of accounting (i.e., Auditing, Financial Accounting and Reporting, Managerial Accounting, Taxation, Accounting information systems, and Other) and whether they believe the findings in their field are reproducible. Next, we ask the same questions for their methodological area (i.e., Analytical, Archival/Field, Experimental, Qualitative, Survey, and Other).

After eliciting respondents' perceptions on reproducibility, a set of questions explores their familiarity and experience with the practice of pre-registration. Lastly, we ask them about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research. The survey ends with a few demographic questions. For a complete overview of the survey questions included in our study, please see Appendix A. All answers can be explored using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard} and the data itself are available in our public \href{https://github.com/joachim-gassen/osacc/}{GitHub repository} .

### Survey Administration and Response Sample

To recruit respondents for our survey, we identified authors who published in the "Top 6" accounting journals, i.e., Accounting, Organizations and Society, Contemporary Accounting Research, Journal of Accounting and Economics, Journal of Accounting Research, Review of Accounting Studies, The Accounting Review, over the period 2016 to 2021. We chose these six accounting journals because they are commonly characterized as the leading accounting journals within the academic accounting community. We realize that this is not an exhaustive list and that there are divergent views about journals within the accounting community. Yet, we believe that, taken together, these journals provide a sufficiently broad target population of accounting academics.

We start compiling the list of authors from 2016 because this is the year that Open Science and, more specifically, the reproducibility of research became a more widespread topic of debate among academics within the social sciences and, presumably, accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017]. After receiving approval from an ethical review board and guaranteeing the anonymity of the participating respondents, we sent out initial invitations and a total of three reminders. We allowed potential respondents to opt out of future emails every time we reached out to them. Please see Appendix A for the invitation emails and all reminders.

@@

Table 1 presents our sample selection procedures. Out of 2,660 potential respondents identified, 118 were excluded due to operational reasons.[^3] Additionally, 206 respondents' initial emails bounced, indicating unreachable email addresses. Among the remaining 2,336 successfully contacted accounting researchers, 391 initiated the study (15.4% of the total emails sent), 254 partially completed it (10.9% of the total emails sent), and 222 fully completed it (8.7% of the total emails sent). For our analyses, we employed a floating sample, which dynamically changes based on specific criteria, to maximize the use of the available data. For most descriptive analyses, we relied on the number of respondents who completed the entire study (n = 222). However, for certain descriptive analyses, depending on the specific question, we utilized a broader sample (n = 229) as seven respondents decided to leave out some of the demographic questions. Since our survey experiment component forms the first part of the study, we use the sample of respondents who completed the study up to that point (n = 254) for analysis.

@@

Table 2 displays response demographics and characteristics based on a sample of up to 229 observations. Panel A reveals that the majority of the respondents is male, 35 years or older (87.8%), specializing in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%). Panel B of Table 2 contrasts our respondent sample with our sampling population. Given the anonymity of our response and the data that we can collect about our population, we can only directly compare the geographic dispersion of our sample. Panel B reveals that, in particular, researchers from North America and Europe are over-represented, and researchers from Asia are under-represented in the sample. Given that response rate assessment is inherently challenging, we generally avoid speculating about potential reasons for this sampling imbalance. However, it seems likely that the study's all-European author team might have positively influenced the European response. While we control for geographical effects in our response (not-tabulated but available using our \href{https://jgassen.shinyapps.io/osacc/}{survey dashboard}) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.
